Performance Optimization of Service Chain for vCPE in Small Networks with OpenFlow Switch

### 2017-03-16 netsoft_paper.tex
Host -> host

This method is illustrated in \ref{fig:mft_qos_rate_host}. In T0, host 1 and host 2 are not limited yet. Because host 2 utilizes a substantial amount of bandwidth from the network in T0–T1  the network administrator sets the host 2 rate limit to 400 Kbps. When the controller receives this request, marked as (a), it creates a meter with meter id = 1 and bandwidth = 400 Kbps and sets the rule in the flow table with the destination MAC address = MAC address of Host 1 and meter = 1. According to our new flow table, it limits the rate of the target host. Then, the traffic from Host 2 is reduced and immediately limited to 400 Kbps. A similar situation occurs for Host 1 in T2. The administrator chooses to set Host 1 under 600 Kbps, marked as (b), and then the traffic from Host 1 is limited to 600 Kbps.

@@

We selected YouTube to verify our function for limiting applications and used three hosts (Host 1, Host 2, and Host 3) in the same network domain. Then, we limited the bandwidth of YouTube in this network domain (i.e., the sum of bandwidths of Host 1, Host 2, and Host 3).

>>>>

This method is illustrated in \ref{fig:mft_qos_rate_host}. In T0, host 1 and host 2 are not limited yet. Because host 2 utilizes a substantial amount of bandwidth from the network in T0–T1  the network administrator sets the host 2 rate limit to 400 Kbps. When the controller receives this request, marked as (a), it creates a meter with meter id = 1 and bandwidth = 400 Kbps and sets the rule in the flow table with the destination MAC address = MAC address of host 1 and meter = 1. According to our new flow table, it limits the rate of the target host. Then, the traffic from host 2 is reduced and immediately limited to 400 Kbps. A similar situation occurs for host 1 in T2. The administrator chooses to set host 1 under 600 Kbps, marked as (b), and then the traffic from host 1 is limited to 600 Kbps.

@@

We selected YouTube to verify our function for limiting applications and used three hosts (host 1, host 2, and host 3) in the same network domain. Then, we limited the bandwidth of YouTube in this network domain (i.e., the sum of bandwidths of host 1, host 2, and host 3).
